### 2018-08-30 scripts/03-methods/README.Rmd
update readmes with github_markdown_nested format
cleanup methods

---
output: github_document
---

```{r include = FALSE}
library(tidyverse)
library(dynbenchmark)

knitr::opts_chunk$set(echo = FALSE)
```

@@

- Compile all the information we have about TI methods
- Group methods into sets of "tools"
- Download and process the information from the QC spread sheet (https://docs.google.com/spreadsheets/d/1Mug0yz8BebzWt8cmEW306ie645SBh_tDHwjVw4OFhlE)
- Create tables and figures to interpret the methods and quality control

@@

>>>>

---
output: dynbenchmark::github_markdown_nested
---

@@

- Compile all the information we have about TI methods
- Characterise the methods with regards to user and developer friendliness (method quality control)
- Characterise the methods with regards to prior information, underlying algorithm, possible detectable trajectory types, ...

@@

```{r, results = "asis"}
dynbenchmark::knit_nest("01-gather_methods_information")
```
